Cycles of the logistic map

### 2013-04-15 doc/pc-ijbc.tex
doc: x^{new} remove () around the subscript
edit the intro of homogeneous linear eqs.

To simplify the calculation, we first change variables \cite{saha} by
%
%\begin{equation}
\[
    x^{(\mathrm{new})} \leftarrow r(x^{(\mathrm{old})} - 1/2),
    \quad R \leftarrow r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{(\mathrm{new})}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of the polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

@@

Instead of solving \refeqs{logmaps} for $x_k$,
  we will derive a set of \emph{homogeneous linear} equations
  of cyclic polynomials of $x_k$
  (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
%
%We know then that
  Now the matrix formed by the coefficients of the homogeneous linear equations
  must have a zero determinant,
  for the cyclic polynomials are not zeros altogether.
%
%As the coefficients are polynomials of $R$ only,
Thus, the zero-determinant condition gives
  the needed polynomial equations of $R$,
whose roots contain all fixed points of $f^n$.
This completes the first step.
%
%Note that we will obtain different equations
%  at the onset and bifurcation points
%  because the coefficients,
%  hence the matrices and determinants,
%  will be different.
%

>>>>

To simplify the calculation, we first change variables \cite{saha} by
%
%\begin{equation}
\[
    x^{\mathrm{new}} \leftarrow r(x^{\mathrm{old}} - 1/2),
    \quad R \leftarrow r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{\mathrm{new}}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of the polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

@@

Instead of solving \refeqs{logmaps} for $x_k$,
  we will derive a set of \emph{homogeneous linear} equations
  $\sum_j A_{ij} C_j = 0$
  regarding cyclic polynomials $\{C_j\}$ of $x_k$
  (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
%
Now the matrix formed by the coefficients $A_{ij}$ of the equations
  must have a zero determinant,
  for the cyclic polynomials $\{C_j\}$ are not zeros altogether.
%
%As the coefficients are polynomials of $R$ only,
Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
  the needed polynomial equation of $R$,
whose roots contain all fixed points of $f^n$.
This completes the first step.
%
%Note that we will obtain different equations
%  at the onset and bifurcation points
%  because the coefficients,
%  hence the matrices and determinants,
%  will be different.
%
